Tesseroids: forward modeling gravitational fields in spherical coordinates

### 2015-03-07 manuscript.tex
Add Valeria and Carla as authors
Better caption for the experiments table

\hypersetup{
    colorlinks=true,
    citecolor=blue,
    linkcolor=blue,
    urlcolor=blue,
    pdfauthor={Uieda et al.},
    pdftitle={Tesseroids: forward modeling gravitational fields in spherical
              coordinates}
}
\title{
    Tesseroids: forward modeling gravitational fields in spherical coordinates
}
\author{
    Leonardo Uieda\footnotemark[1]\footnotemark[2],
    et al.
}

@@

\address{
\footnotemark[1]Universidade do Estado do Rio de Janeiro,
Rio de Janeiro, Brazil.
email: leouieda@gmail.com
\footnotemark[2]Observat\'orio Nacional,
Rio de Janeiro, Brazil.
}

@@

\begin{table*}
\centering
\begin{tabular}{cccc}
    \hline
    ~             & Grid location & Grid height & Tesseroid size \\
    \hline
    Experiment 1  & 89N--90N/0E--1E & 2 km & $1^\circ \times 1^\circ$ \\
    Experiment 2  & 0N--1N/0E--1E & 2 km & $1^\circ \times 1^\circ$ \\
    Experiment 3  & 89N--90N/0E--1E & 260 km & $1^\circ \times 1^\circ$ \\
    Experiment 4  & 60N--90N/0E--30E & 2 km & $30^\circ \times 30^\circ$ \\
    \hline
\end{tabular}
\caption{Parameters of the numerical experiments.}
\label{tbl:experiment}
\end{table*}

>>>>

\hypersetup{
    colorlinks=true,
    citecolor=blue,
    linkcolor=blue,
    urlcolor=blue,
    pdfauthor={Uieda et al.},
    pdftitle={Tesseroids: forward modeling gravitational fields in spherical
              coordinates}
}
\title{
    Tesseroids: forward modeling gravitational fields in spherical coordinates
}
\author{
    Leonardo Uieda\footnotemark[1]\footnotemark[2],
    Val\'eria C. F. Barbosa\footnotemark[2],
    and
    Carla Braitenberg\footnotemark[3]
}

@@

\address{
\footnotemark[1]Universidade do Estado do Rio de Janeiro,
Rio de Janeiro, Brazil.
email: leouieda@gmail.com
\\
\footnotemark[2]Observat\'orio Nacional,
Rio de Janeiro, Brazil.
\\
\footnotemark[3]Department of Mathematics and Geosciences, University of
Trieste, Trieste, Italy
}

@@

\begin{table*}
\centering
\begin{tabular}{cccc}
    \hline
    ~             & Grid location & Grid height & Tesseroid size \\
    \hline
    Experiment 1  & 89N--90N/0E--1E & 2 km & $1^\circ \times 1^\circ$ \\
    Experiment 2  & 0N--1N/0E--1E & 2 km & $1^\circ \times 1^\circ$ \\
    Experiment 3  & 89N--90N/0E--1E & 260 km & $1^\circ \times 1^\circ$ \\
    Experiment 4  & 60N--90N/0E--30E & 2 km & $30^\circ \times 30^\circ$ \\
    \hline
\end{tabular}
\caption{
    Parameters of the numerical experiments to quantify the accuracy of
    the numerical integration.
    All grids had $10\times10$ regularly spaced computation points at a
    constant height.
    Tesseroids used to discretize the spherical shell had 1 km thickness and
    the horizontal dimensions shown in the table.
}
\label{tbl:experiment}
\end{table*}
